Characterizing Stellar Streams by ML

### 2023-08-30 src/tex/ms.tex
[showyourwork] overleaf sync

\newcommand{\package}[1]{\textsc{#1}}
\newcommand{\stream}[1]{#1}
\newcommand{\dataarchive}[1]{\texttt{#1}}
\newcommand{\Gaia}{\dataarchive{Gaia}}
\newcommand{\PanStarrs}{\dataarchive{Pan-STARRS1}}

@@

\section{Introduction} \label{sec:intro}
    %
    Stellar streams are the disrupted
    remnants of globular clusters and satellite galaxies, and their census has
    grown extensively in the Milky Way thanks to all-sky astrometric missions
    like {\it Gaia} and low-surface brightness photometric surveys (\JN{cite}).
    The formation of streams can be traced back to a progenitor cluster (i.e., a
    satellite galaxy or globular cluster), whose stars are gradually lost to the
    tidal field of the host galaxy and extend along a series of similar orbits
    producing tidal tails, which can sometimes span many tens of degrees across
    the sky. This orbital proximity of stars belonging to a stream makes them
    sensitive tracers of the mass distribution of galaxies, sourced by both the
    baryonic and dark matter components.
    % 
    The average properties of a stream (e.g., the mean position and velocity
    track of the tidal tails) can be used to reconstruct the global dark matter
    distribution of the stellar halo (e.g., \JN{cite}), while local variations
    in the stream track and surface density encode information about the
    stream's encounters with baryonic structures such as (e.g.) the stellar bar
    (\JN{cite}), and non-luminous structures like dark matter subhalos
    (\JN{cite}). Importantly, these galactic components span orders of magnitude
    in mass, highlighting the importance of characterizing a population of
    stellar streams both in morphology and kinematics. 
    % 
    While several methods have been developed to model stream properties as a
    function of global halo properties (e.g., flattening and
    orientation;\JN{cite}) and local substructures (e.g., the bar's pattern
    speed and the mass of subhalo perturbers; \JN{cite}), these methods and
    insights often rely on the existence of a homogenized stream-tracer
    population that characterizes the stream across each of the observable
    phase-space dimensions. Additionally, because even the fine-grain properties
    of streams are influenced by the detailed mass distribution of galaxies, it
    is important to propagate errors both in measurement uncertainty and
    membership uncertainty (i.e., which stars belong to the stream versus the
    background) when attempting to model the galaxy. Otherwise, a stream that
    has been poorly characterized could bias constraints on (e.g.) the total
    mass of the galaxy, the dark matter halo shape, and the mass of subhalo
    perturbers. In order to generate more precise constraints on the structure
    of the galaxy, it is therefore imperative that a statistically sound and
    homogenized catalog of stellar streams is produced so that theoretical
    models for the gravitational potential of the galaxy across a large range of
    spatial scales can be constrained. 
    %
    While streams are well described in (e.g.) action angle coordinates or
    $N-$body simulations, these methods relying on prior assumptions about the
    galaxy and its underlying potential. Therefore, it is important to devise
    data-driven methods to characterize stellar streams without appealing to
    strong prior assumptions about the galaxy's structure. 
    % 
    There are a few previous works which have modeled stellar streams in this
    context. \citet{Patrick+2022} developed a data-driven spline-based
    model for modeling the photometric qualities of previously identified
    streams. Their method works by fitting the stream's stellar surface density
    with a series of splines, capturing both surface brightness variations along
    the stream and changes in the position of the stream track and width. Their
    method also utilize a simultaneous ischorone fit to the stream, from which a
    distance modulus can be derived by assuming that the entire stream
    originates from the same stellar population. While this method is very
    successful at characterizing the photometric properties of a stream, it does
    not consider the kinematic dimensions which have become increasing
    well-measured with successive data releases from {\it Gaia}, as well as
    targeted observations. From a population of RR Lyrae stars,
    \citet{Price-Whelan+2019} utilized a mixture model to fit the globular
    cluster stream Pal-5 in the space of proper motions and heliocentric
    distances. The mixture modeling approach enables a simultaneous fit to both
    the stream and background density, enabling better separation of a coherent
    stream from an otherwise noisy background distribution. However, the track
    of the stream in on-sky coordinates is not fit. The method identified 27 RR
    Lyrae stars consistent with being members of the stream. While useful for
    determining the average properties of the stream (e.g., its mean distance
    track), a limited population of RR Lyrae stars are not sufficient to capture
    the fine-grained properties of streams expected to inform constraints on
    (e.g.) a population of perturbers in the galaxy. \JN{are there other
    methods?}
    % 
    Other methods for extracting stellar streams from the data include
    matched-filter approaches, where over-densities in color-magnitude space are
    inspected as possible clusters undergoing tidal stripping \JN{cite the many
    key papers using this method}. While the matched-filter technique has been
    extremely successful at stream discovery, it is not equipped to characterize
    streams at the level of detailed necessary to inform precise constraints on
    the potential of the galaxy and its substructure.
    % 
    In order to address the need for a flexible model of stellar streams both in
    photometric and kinematic spaces, in this work we develop a new method for
    characterizing streams and quantifying the membership probability of
    possible stream stars. Our approach provides several key advantage over
    previous stream modeling efforts, specifically in its ability to jointly
    model the kinematic and photometric properties of streams simultaneously.
    Furthermore, our method is well-suited to fitting streams with only partial
    or incomplete phase-space or photometric observations, enabling a full
    characterization of streams insofar as the available data allows.

@@

        \begin{figure*}
            \script{mock/plot/results.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
            \caption{
                %
                \textbf{Top panel:}%
                    The stream mixture coefficient $f(\phi_1)$ (black dotted line)
                    predicted by the model, overplotted on the true stream fraction
                    (black-outlined histogram), calculated as the ratio of stream
                    stars to total stars in 55 bins over the $\phi_1$ range of the
                    isochrone.  \textbf{Middle panel: }%
                    $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data color
                    and transparency is set by the model's MLE stream probability
                    (with dropout turned off). Plotted behind the data are the true
                    labels for the stream stars (large black circles).  The true
                    labels exactly limn the model-identified stream stars.  The MLE
                    stream track (black dashed line) is over-plotted on the
                    probability-colored data.
                %
                \textbf{Lower panel 3: }%
                    $\varpi_2(\phi_1)$ over the full range of $\phi_1$. Like for
                    $\phi_2$, the data color and transparency is set by the MLE
                    probability, with the true labels (large black circles)
                    under-plotted and MLE track (black dashed line) over-plotted.
                %
                \textbf{Upper Histograms: }%
                    $\phi_2$ histograms for each model component (blue background,
                    red stream), in 4 $\phi_1$ ranges across the data set.  The
                    height of each bin is the probability-weighted density.  The
                    background is a uniform distribution, while the stream is a
                    Gaussian. In projection across the $\phi_1$ range it can appear
                    multi-modal (panel 2) if there are large gaps or `smeared' out
                    (panel 3) if the Gaussian's mean changes significantly over the range.
                %
                \textbf{Upper Middle Histograms: }%
                    Parallax $\varpi$ histograms for each model component (blue
                    background, red stream), in 4 $\phi_1$ ranges across the data
                    set.  The height of each bin is the probability-weighted
                    density.
                %
                \textbf{Lower Middle and Lower Histograms:}%
                    Photometric coordinate $(g, r)$ plots for each model component
                    in 4 $\phi_1$ ranges across the data set. The top row plots the
                    stream stars (red) over the background. The lower row plots the
                    background stars (blue) over the stream stars to show that the
                    how the two distributions mix.
                % 
            }
            \label{fig:mock_data_result}
            TODO:
            \begin{enumerate}
                \item the linear density in the stream-fraction plot
            \end{enumerate}
        \end{figure*}

@@

        We find that the stream is successfully recovered in both astrometric and
        photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ of stream
        stars being recovered with membership probability greater than $80\%$.
        In the bottom two rows of \autoref{fig:mock_data_result} we illustrate the
        synthetic data color-coded by stream membership probability (top) and
        background membership probability (background) for different $\phi_1$
        slices. Importantly, the photometric portion of the mixture model
        successfully identifies the stream in magnitude space, showing a high stream
        membership probability where the stream is present, and a low probability
        ($\sim 0$) where the stream is absent.
        The false positive rate (i.e., stars misidentified as stream members) for this test
        is found to be $\variable{output/mock/falseident_variable.txt}\%$ when cutting on
        the 80\% membership probability threshold.
        % The perfect recovery rate and low false identification rate demonstrate the efficacy
        % of this method.

@@

        We utilize data from \Gaia{} DR3 for the astrometric coordinates of
        each star. 
        To obtain more accurate color information, we cross-match the \Gaia{}
        field on \PanStarrs{} \citep{PanSTARRS1} using 
        \Gaia's provided \texttt{Best-neighbors} catalog.
        To limit the field to a region known to contain GD-1 we adopt broad cuts
        on the cross-matched data. We perform these rough cuts by requiring
        the data lie within the phase-space cube:
        \begin{itemize}
            \item $\phi_1 \in [-100, 40] \ \rm{\degree}$,
            \item $\phi_2 \in [-9, 5] \rm{\degree}$,
            \item $\varpi \in [-10, 1] \ \rm{mas}$,
            \item $\rm{bp-rp} \in [-1, 3] \ \rm{mag}$
            \item $g, r \in [0, 50] \ \rm{mag}$, and not \texttt{null}.
        \end{itemize}
        where, we use Gala's \citep{gala, galav1.3} \texttt{GD1Koposov10} frame
        \citep{Koposov+2010} to define $\phi_1$, $\phi_2$, and associated proper motions.
        For downloading purposes, we split the query into 10 sub-regions,
        in even $\phi_1$ increments. A plot of the $\phi_1, \phi_2$ regions is included
        in the \href{\GitHubURL{}}{\package{ShowYourWork}} repository.
        Stream-specific coordinates ($\phi_1, \phi_2$) are not included in \Gaia.
        One could embed the coordinate transform in the ADQL \citep{ADQL2.0},
        or define great-circle arcs in ICRS \citep{ICRS1997}. Since only rough
        cuts are required and since the boxes are sufficiently small for a reasonable flat-sky
        approximation  we simply translate the ($\phi_1, \phi_2$) sub-region boxes to ICRS.
        We correct the \PanStarrs{} photometry for dust extinction
        using the \textit{Bayestar19} \citep{Green+2019} models in the \package{dustmaps} package \citep{Green2018}.
        \textit{Bayestar19 is a three-dimensional dust map of the Milky Way
        for which we use \Gaia's parallax distance information.
        We include the $1-\sigma$ errors as a source of uncertainty
        in $\Sigma_n$, the per-star photometric uncertainty.
        % TODO: actually implement that in the model
        The result is a field populated by \variable{output/gd1/ndata_variable.txt} stars, from which we would
        like to identify stream members.

        In \autoref{fig:gd1-data_selection} we create data masks for a more refined
        selection around the stream.

        We make proper motion selection boxes at box corners $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, and $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \ \unit{mas/yr}$,

        \begin{figure*}[h]
            \script{gd1/plot/data_selection.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/gd1/data_selection.pdf}
            \caption{%
                Data selections for \stream{GD-1}, within the data cube described
                in \autoref{sub:results_gd1:data}.
                %
                \textbf{Row 1 Panels:}
                Proper motion selection boxes in red and yellow.
                The right plot
                %
                \textbf{Row 2 Panels:}
                Photometric selection (blue curve). The selection is based on
                a 12 Gyr, [Fe/H] = -1.3 MIST isochrone, buffered by 0.2 dex.
                % 
                \textbf{Row 3 Panels:}
                Applying the red astrometric and blue photometric selections, plotted
                for astrometric coordinates $\phi_2, \varpi, \mu_{\phi_1}, \mu_{\phi_2}$.
                % 
                \textbf{Row 4 Panels:}
                Applying the yellow astrometric and blue photometric selections, plotted
                for the same astrometric coordinates as the above row.
            }
            \label{fig:gd1-data_selection}
        \end{figure*}

@@

        \begin{figure*}[h]
            \script{gd1/plot/results_full.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/gd1/results_full.pdf}
            \caption{CAPTION}
            TODO:
            \begin{itemize}
                \item Add plot of the stream linear density
                \item Color palette for the spur
                \item more subtle stream MLE path
                \item rerun model with larger pmphi2 sigma
                \item add the isochrones to the cmd plots
            \end{itemize}
            \label{fig:gd1-results-full}
        \end{figure*}

>>>>

\newcommand{\code}[1]{\textsc{#1}}
\newcommand{\package}[1]{\code{#1}}
\newcommand{\stream}[1]{#1}
\newcommand{\dataarchive}[1]{\texttt{#1}}
\newcommand{\Gaia}{\dataarchive{Gaia}}
\newcommand{\PanStarrs}{\dataarchive{Pan-STARRS1}}

@@

\section{Introduction} \label{sec:intro}
    %
    Stellar streams are the disrupted
    remnants of globular clusters and satellite galaxies, and their census has
    grown extensively in the Milky Way thanks to all-sky astrometric missions
    like {\it Gaia} and low-surface brightness photometric surveys (\JN{cite}).
    The formation of streams can be traced back to a progenitor cluster, whose stars are gradually lost to the
    tidal field of the host galaxy and extend along a series of similar orbits
    producing tidal tails, which can sometimes span several tens of degrees across
    the sky. The orbital proximity of stars belonging to a stream makes them
    sensitive tracers of the mass distribution of galaxies, sourced by both the
    baryonic and dark matter components.

    The average properties of a stream (e.g., the mean position and velocity
    track of the tidal tails) can be used to reconstruct the global dark matter
    distribution of the stellar halo (e.g., \JN{cite}), while local variations
    in the stream track and surface density encode information about the
    stream's encounters with baryonic structures such as (e.g.) the stellar bar
    (\JN{cite}), and non-luminous structures like dark matter subhalos
    (\JN{cite}). Importantly, these galactic components span orders of magnitude
    in mass and spatial extent, highlighting the sensitivity of streams in constraining the structure of the galaxy.

    While several methods have been developed to model stream properties as a
    function of global halo characteristics (e.g., flattening and
    orientation;\JN{cite}) and local substructures (e.g., the bar's pattern
    speed and the mass of subhalo perturbers; \JN{cite}), these methods often rely on the existence of a homogenized stream-tracer
    population that characterizes a given stream across each of the observable
    phase-space dimensions. Additionally, because even the fine-grain properties
    of streams are influenced by the detailed mass distribution of its host galaxy, it
    is important to propagate errors both in measurement uncertainty and
    membership uncertainty (i.e., which stars belong to the stream versus the
    background) when attempting to model a stream. Otherwise, a poorly characterized stream could bias constraints on (e.g.) the total
    mass of the galaxy, the dark matter halo shape, and the mass of subhalo
    perturbers. In order to generate more precise constraints on the structure
    of the galaxy, it is therefore imperative that a statistically sound and
    homogenized catalog of stellar streams is produced.

    While streams are well described in (e.g.) action angle coordinates or
    $N-$body simulations, these methods rely on prior assumptions about the
    galaxy and its underlying gravitational potential. Therefore, it is necessary to devise
    data-driven methods to characterize stellar streams without appealing to
    strong prior assumptions about the galaxy's structure.

    There are a few previous works which have modeled stellar streams in this
    context. \citet{Patrick+2022} developed a data-driven spline-based
    method for modeling the photometric properties and on-sky positions of previously identified
    streams. Their method works by fitting the stream's stellar surface density
    with a series of splines, capturing both surface brightness variations along
    the stream and changes in the position of the stream track and width. Their
    method also utilize a simultaneous isochrone fit to a given stream, from which a
    distance modulus can be derived. While this method is very
    successful at characterizing the photometric properties of a stream, it does
    not consider the kinematic dimensions which have become increasingly
    well-measured with successive data releases from {\it Gaia}, as well as
    targeted observations. From a population of RR Lyrae stars,
    \citet{Price-Whelan+2019} utilized a mixture model to fit the globular
    cluster stream Pal-5 in the space of proper motions and heliocentric
    distances. The mixture modeling approach enables a simultaneous fit to both
    the stream and background density, allowing for better separation of the stream from the background distribution. However, the track
    of the stream in on-sky coordinates is not fit. The method identified 27 RR
    Lyrae stars consistent with being members of the stream. While useful for
    determining the average properties of a stream (e.g., its mean distance
    track), a limited population of RR Lyrae stars are not sufficient to capture
    the small-scale properties of streams expected to inform constraints on
    (e.g.) a population of perturbers in the galaxy. \JN{are there other
    methods?}

    Other methods for extracting stellar streams from the data include
    matched-filter approaches, where over-densities in color-magnitude space are
    inspected as possible clusters undergoing tidal stripping \JN{cite the many
    key papers using this method}. While the matched-filter technique has been
    extremely successful in stream discovery, it is not equipped to characterize
    streams at the level of detailed necessary to inform precise constraints on
    the potential of the galaxy and its substructure.

    In order to address the need for a flexible model of stellar streams both in
    photometric and kinematic spaces, in this work we develop a new method for
    characterizing streams and quantifying the membership probability of
    possible stream stars. Our approach provides several key advantage over
    previous stream modeling efforts, specifically in its ability to jointly
    model the kinematic and photometric properties of streams simultaneously.
    Furthermore, our method is well-suited to fitting streams with only partial
    or incomplete phase-space or photometric observations, enabling a full
    characterization of streams insofar as the available data allows. We do not rely on assumptions about the potential of the galaxy, and utilize mixture density nextworks to flexibly capture the qualities of a stream.

@@

        \begin{figure*}
            \script{mock/plot/results.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
            \caption{
                %
                \textbf{Top panel: }%
                    The stream mixture coefficient $f(\phi_1)$ (black dotted line)
                    predicted by the model, overplotted on the true stream fraction
                    (black-outlined histogram), calculated as the ratio of stream
                    stars to total stars in 55 bins over the $\phi_1$ range of the
                    isochrone.  \textbf{Middle panel: }%
                    $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data color
                    and transparency is set by the model's MLE stream probability
                    (with dropout turned off). Plotted behind the data are the true
                    labels for the stream stars (large black circles).  The true
                    labels exactly limn the model-identified stream stars.  The MLE
                    stream track (black dashed line) is over-plotted on the
                    probability-colored data.
                %
                \textbf{Lower panel 3: }%
                    $\varpi_2(\phi_1)$ over the full range of $\phi_1$. Like for
                    $\phi_2$, the data color and transparency is set by the MLE
                    probability, with the true labels (large black circles)
                    under-plotted and MLE track (black dashed line) over-plotted.
                %
                \textbf{Upper Histograms: }%
                    $\phi_2$ histograms for each model component (blue background,
                    red stream), in 4 $\phi_1$ ranges across the data set.  The
                    height of each bin is the probability-weighted density.  The
                    background is a uniform distribution, while the stream is a
                    Gaussian. In projection across the $\phi_1$ range it can appear
                    multi-modal (panel 2) if there are large gaps or `smeared' out
                    (panel 3) if the Gaussian's mean changes significantly over the range.
                %
                \textbf{Upper Middle Histograms: }%
                    Parallax $\varpi$ histograms for each model component (blue
                    background, red stream), in 4 $\phi_1$ ranges across the data
                    set.  The height of each bin is the probability-weighted
                    density.
                %
                \textbf{Lower Middle and Lower Histograms:}%
                    Photometric coordinate $(g, r)$ plots for each model component
                    in 4 $\phi_1$ ranges across the data set. The top row plots the
                    stream stars (red) over the background. The lower row plots the
                    background stars (blue) over the stream stars to show that the
                    how the two distributions mix.
                % 
            }
            \label{fig:mock_data_result}
            TODO:
            \begin{enumerate}
                \item the linear density in the stream-fraction plot
            \end{enumerate}
        \end{figure*}

@@

        We find that the stream is successfully recovered in both astrometric and
        photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ of stream
        stars being recovered with membership probability greater than $80\%$.
        In the bottom two rows of \autoref{fig:mock_data_result} we illustrate the
        synthetic data color-coded by stream membership probability (top) and
        background membership probability (background) for different $\phi_1$
        slices. Importantly, the photometric portion of the mixture model
        successfully identifies the stream in magnitude space, showing a high stream
        membership probability where the stream is present, and a low probability
        ($\sim 0$) where the stream is absent.
        The false positive rate (i.e., stars misidentified as stream members) for this test
        is found to be $\variable{output/mock/falseident_variable.txt}\%$ (3 stars) when cutting on
        the 80\% membership probability threshold.
        % The perfect recovery rate and low false identification rate demonstrate the efficacy
        % of this method.

@@

        We utilize data from \Gaia{} DR3 for the astrometric coordinates of
        each star. 
        To obtain more accurate color information, we cross-match the \Gaia{}
        field on \PanStarrs{} \citep{PanSTARRS1} using 
        \Gaia's provided \texttt{Best-neighbors} catalog.
        To limit the field to a region known to contain \stream{GD-1} we adopt broad cuts
        on the cross-matched data. We perform these rough cuts by requiring
        the data lie within the phase-space cube:
        \begin{itemize}
            \item $\phi_1 \in [-100, 40] \ \rm{\degree}$,
            \item $\phi_2 \in [-9, 5] \rm{\degree}$,
            \item $\varpi \in [-10, 1] \ \rm{mas}$,
            \item $\rm{bp-rp} \in [-1, 3] \ \rm{mag}$
            \item $g, r \in [0, 50] \ \rm{mag}$, and not \texttt{null}.
        \end{itemize}
        where, we use \package{gala}'s \citep{gala, galav1.3} \code{GD1Koposov10} frame
        \citep{Koposov+2010} to define $\phi_1$, $\phi_2$, and associated proper motions.
        For downloading purposes, we split the query into 10 sub-regions,
        in even $\phi_1$ increments. A plot of the $\phi_1, \phi_2$ regions is included
        in the \href{\GitHubURL{}}{\package{ShowYourWork}} repository.
        Stream-specific coordinates ($\phi_1, \phi_2$) are not included in \Gaia.
        One could embed the coordinate transform in the ADQL \citep{ADQL2.0},
        or define great-circle arcs in ICRS \citep{ICRS1997}. Since only rough
        cuts are required and since the sub-region boxes are sufficiently small for a reasonable flat-sky
        approximation  we simply translate the ($\phi_1, \phi_2$) boxes to ICRS.
        We correct the \PanStarrs{} photometry for dust extinction
        using the \textit{Bayestar19} \citep{Green+2019} models in the \package{dustmaps} package \citep{Green2018}.
        \textit{Bayestar19} is a three-dimensional dust map of the Milky Way
        for which we use \Gaia's parallax distance information.
        We include the $1-\sigma$ errors as a source of uncertainty
        in $\mbs{\Sigma}_n$, the per-star photometric uncertainty.
        % TODO: actually implement that in the model
        The result is a field populated by \variable{output/gd1/ndata_variable.txt} stars,
        from which we would like to identify stream members.

        We create data masks for a more refined selection around \stream{GD-1}.
        The two mask types, proper motion and photometric,
        are show in \autoref{fig:gd1-data_selection}.
        The proper motion masks select rectangular regions, containing the primary overdensity
        of \stream{GD-1} and a surrounding area following the tail of the distribution.
        The tighter mask (red) has corners $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, while the larger mask (yellow) has $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \ \unit{mas/yr}$.
        In photometric coordinates we define a mask around
        % TODO: make these variables, like in mock
        a 12 Gyr, [Fe/H] = -1.3 isochrone at a distance of 7.8 kpc. The selection region is a 0.2 dex orthogonal buffer around the MIST isochrone \citep[using]{brutus}, which
        is illustrated in the 2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}.
        In addition, to avoid detailed modeling of the completeness as a term in $\prior_{obs}$ (from \autoref{isochrone_prior_components}) we mask out photometry with $G_{\Gaia{}} > 20$.
        With combinations of these masks the stream has much larger signal-to-noise, though
        is still only a small percent of the total data.

        \begin{figure*}[h]
            \script{gd1/plot/data_selection.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/gd1/data_selection.pdf}
            \caption{%
                Data selections for \stream{GD-1}, within the data cube described
                in \autoref{sub:results_gd1:data}.
                %
                \textbf{Row 1 Panels:}
                Proper motion selection boxes in red and yellow.
                The right plot shows the application of these selections.
                \stream{GD-1} is apparent from around $-60$ to $-10$ deg in the red
                selection and present, if less clearly, in the yellow selection.
                %
                \textbf{Row 2 Panels:}
                Photometric selection (blue curve). The selection is based on
                a 12 Gyr, [Fe/H] = -1.3 MIST isochrone, buffered by 0.2 dex.
                The right plot shows the application of this selection. By eye, the stream
                is a small overdensity extending from $-50$ to $0$ deg.
                % 
                \textbf{Row 3 Panels:}
                Applying the combination of red astrometric and blue photometric selections,
                plotted for astrometric coordinates $\phi_2, \varpi, \mu_{\phi_1}, \mu_{\phi_2}$.
                The stream is an identifiable overdensity in all phase-space coordinates
                except $\varpi$ where the errors are significant.
                % 
                \textbf{Row 4 Panels:}
                Applying the yellow astrometric and blue photometric selections, plotted
                for the same astrometric coordinates as the above row.
                In these coordinates the stream is clearly observable in $\phi_2$ and very
                faintly in $\mu_{\phi_1}^*$.
            }
            \label{fig:gd1-data_selection}
        \end{figure*}

@@

        \begin{figure*}[h]
            \script{gd1/plot/results_full.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/gd1/results_full.pdf}
            \caption{CAPTION}
            \label{fig:gd1-results-full}
            TODO:
            \begin{itemize}
                \item Add plot of the stream linear density
                \item Color palette for the spur
                \item more subtle stream MLE path
                \item rerun model with larger pmphi2 sigma
                \item add the isochrones to the cmd plots
            \end{itemize}
        \end{figure*}
